\documentclass{article}
\usepackage[english]{babel}
\usepackage[calc,useregional,showdow]{datetime2}
\usepackage{titletoc}
\dottedcontents{section}[1.5in]{\bfseries\large}{1.5in}{10pt}

\usepackage{xparse}
\NewDocumentCommand{\datesec}{o m m}{%
    \renewcommand\thesection{\DTMdate{#2}}
    \IfNoValueTF{#1}
        {\section{#3}}
        {\section[#1]{#3}}
}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, %set true if you want colored links
    linktoc=all,     %set to all if you want both sections and subsections linked
    linkcolor=blue,  %choose some color if you want links to stand out
}
\begin{document}
\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{DevLog}

       \vspace{0.5cm}
        Devlog for PyLearnGTK

       \vspace{1.5cm}

       \textbf{Arseni Yamnii}

       \vfill


       \vspace{0.8cm}



       StackOverflow\\
       Git\\
       Linux\\
       Python3\\
       LaTex\\
       GTK\\
       2020

   \end{center}
\end{titlepage}
\tableofcontents
\newpage
\datesec{2020-04-29}{create DevLog}
here il starting write dev log with all my thinks(misly in russian) about this project
\newpage
\datesec{2020-05-02}{LaTex}
Start using Latex
And so... I create my template for DevLog. It is like diary for application. Here i write some tips and triks)).\\
I think sometimes i create script to integrate this tis to Documentation. Maby with some Tags, etc.\\
Yes, it is long project... with UML and texts. But it pretty shit functionals. BUT mayby sometimes it get more functional, to got more popularity.\\
TODO:
\begin{itemize}
  \item Create UML diagram with TikzUML. Yes in latex.....
  \item Find examples to python with GTK
  \item Create GTK UI
  \item create tests to program
\end{itemize}
\newpage
\datesec{2020-05-03}{UML day one}
Few days ago i find latex package TIKZ-UML. this package was created for create UML diagrams in latex. I think it is the best tool for create uml, because for transfer source to another achine, you only need to transfer few files. .tex file, and library tikz-uml. And then compile to format what you want.\\
TODO:
\begin{itemize}
  \item crete folder for code examples
  \item look throgt tikz-uml example code, and create own UML diagrams for project. I dont know why, but for new expierance
\end{itemize}
\newpage
\datesec{2020-05-05}{Little tis about UML}
UML got 15 diagrams :\\
\begin{itemize}
  \item class - DONE
  \item component
  \item composite structure
  \item collaboration
  \item deployment
  \item object
  \item package 
  \item profile
  \item activity
  \item state machine
  \item use case
  \item communication
  \item interaction overview
  \item sequence
  \item timing
\end{itemize}
I need learn all about this 15 diagrams, and create exampples, or working diagrams to my project. For new expiarence.
\datesec{2020-05-07}{UML class diagram}
I create i think good class diagram to first try. When i learn GTK, and UML more, i recreate it diagram. Tikz-uml goood))
\datesec{2020-05-08}{Ready with UM-class, and note about Sphinx}
Few day ago, i see, that Linux kernel used Sphinx as auto-documentation tool. I need learn more about sphinx
UPD: Right now i undestand, that i dont use Software Development Cycle. I need that.
\begin{itemize}
  \item plannning
  \item analysis
  \item design
  \item implementation
  \item testing and integration
  \item maintenance
\end{itemize}
\end{document}

